True versus apparent shapes of astrophysical bow shocks

### 2016-05-31 papers/Paper1/sec-application.tex
Updated table in paper

\begin{table*}
  \caption{Fitted arc parameters for proplyd bowshocks}
  \label{tab:arc-fits} 
\newcommand\C[1]{\multicolumn{1}{c}{#1}}
\begin{tabular}{llrllllrlll}\toprule
             &          & \multicolumn{3}{c}{\dotfill Observed \dotfill}              & \multicolumn{6}{c}{\dotfill Model fits \dotfill} \\ 
  \C{OW}     & \C{Name} & \(D'\) &\C{ \(R_0'/D'\) }&\C{ \((R_c'/R_0')_{\mathrm{shape}}\) }&\C{ \((R_c'/R_0')_{\mathrm{flux}}\) }&\C{ \(\beta\) }&\C{ \(\xi\) }&\C{ \(|i|\) }&\C{ \(D\) }&\C{ \(R_0/D\)}\\
  \C{(1)}& \C{ (2) }&\C{ (3)    }&\C{    (4)      }&\C{              (5)           }&\C{           (6)             }&\C{     (7)   }&\C{   (8)   }&\C{   (9) }&\C{  (10) }&\C{   (11)} \\
\midrule     
168-328  &     & 6.8 & \(0.152 \pm 0.001\) & \(1.42 \pm 0.09\) & \(1.45 \pm 0.05\) & \(0.018 \pm 0.003\) & 0.4--0.6 & \(33 \pm 3\) & \(0.017 \pm 0.001\) & \(0.115 \pm 0.005\)\\
169-338  &     & 16.5 & \(0.059 \pm 0.001\) & \(1.76 \pm 0.48\) & \(1.50 \pm 0.05\) & \(0.002 \pm 0.001\) & 0.8--0.8 & \(43 \pm 8\) & \(0.049 \pm 0.006\) & \(0.035 \pm 0.005\)\\
177-341  & HST1& 25.6 & \(0.144 \pm 0.001\) & \(1.21 \pm 0.02\) & \(1.21 \pm 0.02\) & \(0.018 \pm 0.003\) & 0.1--0.2 & \(30 \pm 5\) & \(0.064 \pm 0.003\) & \(0.115 \pm 0.005\)\\
180-331  &     & 25.1 & \(0.061 \pm 0.007\) & \(1.30 \pm 0.04\) & \(1.27 \pm 0.05\) & \(0.003 \pm 0.001\) & 0.4--0.4 & \(35 \pm 7\) & \(0.067 \pm 0.007\) & \(0.047 \pm 0.005\)\\
167-317  & LV2 & 7.8 & \(0.305 \pm 0.025\) & \(0.81 \pm 0.28\) & \(1.50 \pm 0.1\) & \(0.085 \pm 0.015\) & 0.1--0.2 & \(13 \pm 13\) & \(0.018 \pm 0.001\) & \(0.225 \pm 0.005\)\\
         & LV2b& 7.0 & \(0.097 \pm 0.002\) & \(2.00 \pm 0.62\) & \(1.63 \pm 0.08\) & \(0.008 \pm 0.003\) & 0.8--0.8 & \(28 \pm 13\) & \(0.018 \pm 0.002\) & \(0.078 \pm 0.012\)\\
163-317  & LV3 & 6.9 & \(0.334 \pm 0.002\) & \(1.81 \pm 0.11\) & \(1.81 \pm 0.15\) & \(0.075 \pm 0.025\) & 0.6--0.8 & \(35 \pm 5\) & \(0.018 \pm 0.001\) & \(0.205 \pm 0.025\)\\
161-324  & LV4 & 6.2 & \(0.186 \pm 0.002\) & \(2.59 \pm 0.24\) & \(2.05 \pm 0.07\) & \(0.040 \pm 0.014\) & 0.8--1.0 & \(18 \pm 12\) & \(0.014 \pm 0.001\) & \(0.160 \pm 0.028\)\\
168-323  & LV5 & 9.4 & \(0.213 \pm 0.002\) & \(1.57 \pm 0.07\) & \(1.60 \pm 0.07\) & \(0.055 \pm 0.005\) & 0.2--0.4 & \(20 \pm 5\) & \(0.022 \pm 0.001\) & \(0.190 \pm 0.010\)\\
\bottomrule
\end{tabular}
\begin{minipage}{0.95\linewidth}
  Notes --
%
  Col.~(1): Source ID \citep{ODell:1994a}.
%
  Col.~(2): Alternative name of source.
% 
  Col.~(3): Projected distance from \thC{}, arcseconds.
%
  Col.~(4): Apparent shell outer radius along axis, normalized to
  projected distance, with \(\pm 1\sigma\) uncertainties, determined
  from circle fits described in \S~\ref{sec:methodology}.
% 
  Col.~(5): Apparent shell radius of curvature, normalized to radius
  along axis, with \(\pm 1\sigma\) uncertainties, determined from
  circle fits described in \S~\ref{sec:methodology}.
% 
  Col.~(6): As Col.~(5) but applying the additional requirement that
  the proplyd surface brightness from model fits should agree with the
  theoretical prediction.
%
  Col.~(7): Proplyd-to-O~star wind momentum ratio (see \S~\ref{sec:crw-scenario}). 
% 
  Col.~(8): Proplyd wind anisotropy factor.
% 
  Col.~(9): Inclination to plane of sky, degrees.
% 
  Col.~(10): True distance from \thC{}, parsecs.
%
  Col.~(11): True shell radius along axis, normalized to distance.

>>>>

\begin{table*}
  \caption{Fitted arc parameters for proplyd bowshocks}
  \label{tab:arc-fits} 
\newcommand\C[1]{\multicolumn{1}{c}{#1}}
\begin{tabular}{llrllllrlll}\toprule
             &          & \multicolumn{3}{c}{\dotfill Observed \dotfill}              & \multicolumn{6}{c}{\dotfill Model fits \dotfill} \\ 
  \C{OW}     & \C{Name} & \(D'\) &\C{ \(R_0'/D'\) }&\C{ \((R_c'/R_0')_{\mathrm{shape}}\) }&\C{ \((R_c'/R_0')_{\mathrm{flux}}\) }&\C{ \(\beta\) }&\C{ \(\xi\) }&\C{ \(|i|\) }&\C{ \(D\) }&\C{ \(R_0/D\)}\\
  \C{(1)}& \C{ (2) }&\C{ (3)    }&\C{    (4)      }&\C{              (5)           }&\C{           (6)             }&\C{     (7)   }&\C{   (8)   }&\C{   (9) }&\C{  (10) }&\C{   (11)} \\
\midrule     
 168-328  &            &    6.8  &  $0.152 \pm 0.001$  &  $1.42 \pm 0.09$   &  $1.45 \pm 0.05$     &  $0.018 \pm 0.003$  &  0.4 -- 0.6  &  $33 \pm 3$   &  $0.017 \pm 0.001$  &  $0.115 \pm 0.005$  \\
 169-338  &            &  16.4  &  $0.059 \pm 0.001$  &  $1.76 \pm 0.48$   &  $1.50 \pm 0.05$     &  $0.002 \pm 0.001$  &  0.8 -- 0.8  &  $43 \pm 8$   &  $0.049 \pm 0.006$  &  $0.035 \pm 0.005$  \\
 177-341  & HST1   & 25.6  &  $0.144 \pm 0.001$  &  $1.21 \pm 0.02$   &  $1.25 \pm 0.02$     &  $0.018 \pm 0.003$  &  0.1 -- 0.2  &  $30 \pm 5$   &  $0.064 \pm 0.003$  &  $0.115 \pm 0.005$  \\
 180-331  &             &  25.1  &  $0.061 \pm 0.007$  &  $1.30 \pm 0.05$   &  $1.27 \pm 0.05$     &  $0.003 \pm 0.001$  &  0.4 -- 0.4  &  $35 \pm 7$   &  $0.066 \pm 0.007$  &  $0.047 \pm 0.005$  \\
 167-317  &  LV2     &    7.8  &  $0.305 \pm 0.025$  &  $0.81 \pm 0.28$   &  $1.50 \pm 0.1$      &  $0.085 \pm 0.015$  &  0.1 -- 0.2  &  $13 \pm 13$  &  $0.017 \pm 0.001$  &  $0.225 \pm 0.005$  \\
               & LV2b    &   7.2  &  $0.097 \pm 0.002$  &  $2.00 \pm 0.62$   &  $1.63 \pm 0.08$     &  $0.008 \pm 0.003$  &  0.8 -- 0.8  &  $28 \pm 13$  &  $0.018 \pm 0.002$  &  $0.078 \pm 0.013$  \\
 163-317  & LV3      &   6.9  &  $0.334 \pm 0.002$  &  $1.81 \pm 0.12$   &  $1.85 \pm 0.15$     &  $0.075 \pm 0.025$  &  0.6 -- 0.8  &  $35 \pm 5$   &  $0.018 \pm 0.001$  &  $0.205 \pm 0.025$  \\
 161-324  & LV4      &   6.2  &  $0.186 \pm 0.002$  &  $2.59 \pm 0.24$   &  $2.05 \pm 0.07$     &  $0.040 \pm 0.014$  &  0.8 -- 1.0  &  $18 \pm 12$  &  $0.014 \pm 0.001$  &  $0.160 \pm 0.028$  \\
 168-323  & LV5      &   9.6  &  $0.213 \pm 0.002$  &  $1.57 \pm 0.07$   &  $1.60 \pm 0.07$     &  $0.055 \pm 0.005$  &  0.2 -- 0.4  &  $20 \pm 5$   &  $0.022 \pm 0.001$  &  $0.190 \pm 0.010$  \\
\bottomrule
\end{tabular}
\begin{minipage}{0.95\linewidth}
  Notes --
%
  Col.~(1): Source ID \citep{ODell:1994a}.
%
  Col.~(2): Alternative name of source.
% 
  Col.~(3): Projected distance from \thC{}, arcseconds.
%
  Col.~(4): Apparent shell outer radius along axis, normalized to
  projected distance, with \(\pm 1\sigma\) uncertainties, determined
  from circle fits described in \S~\ref{sec:methodology}.
% 
  Col.~(5): Apparent shell radius of curvature, normalized to radius
  along axis, with \(\pm 1\sigma\) uncertainties, determined from
  circle fits described in \S~\ref{sec:methodology}.
% 
  Col.~(6): As Col.~(5) but applying the additional requirement that
  the proplyd surface brightness from model fits should agree with the
  theoretical prediction.
%
  Col.~(7): Proplyd-to-O~star wind momentum ratio (see \S~\ref{sec:crw-scenario}). 
% 
  Col.~(8): Proplyd wind anisotropy factor.
% 
  Col.~(9): Inclination to plane of sky, degrees.
% 
  Col.~(10): True distance from \thC{}, parsecs.
%
  Col.~(11): True shell radius along axis, normalized to distance.
